Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-01-11 paper/author_disambiguaton.tex
modifying the abstract
Adding a few ideas to the abstract

\numberofauthors{4} 
\author{
\alignauthor
Gilles Louppe\\
       \affaddr{CERN, Switzerland}\\
       \email{g.louppe@cern.ch}
\alignauthor
Hussein T. Al-Natsheh\\
       \affaddr{ISH-LYON, CNRS, France}\\
       \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
\alignauthor
Mateusz Susik\\
       \affaddr{University of Warsaw}\\
       \email{msusik@student.uw.edu.pl}
\alignauthor
\and
Eamonn Maguire\\
       \affaddr{CERN, Switzerland}\\
       \email{eamonn.james.maguire@cern.ch}
}

@@

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by the same person, accounting
for potential homonyms and/or synonyms.
Among solutions to this problem, digital libraries are increasingly offering tools
for authors to manually curate their publications and claim those that are theirs.
Indirectly, these tools allow for the inexpensive collection of large annotated training
data, which can be further leveraged to build a complementary automated
disambiguation system capable of inferring patterns for identifying
publications written by the same person.
Building on more than 1 million publicly released crowdsourced annotations,
we propose an automated author disambiguation solution exploiting this data (i) to learn
an accurate classifier for identifying coreferring authors and (ii) to guide the clustering
of scientific publications by distinct authors in a semi-supervised way.
To the best of our knowledge, our analysis is the first to be carried out on data of
this size and coverage.
With respect to the state of the art, we validate the general pipeline used in most existing
solutions, and improve by: (i) proposing phonetic-based blocking strategies, thereby
increasing recall; and (ii) adding strong ethnicity-sensitive features for learning a linkage
function, thereby tailoring disambiguation to non-Western author names whenever necessary.
\end{abstract}

>>>>

\numberofauthors{4} 
\author{
\alignauthor
Gilles Louppe\\
       \affaddr{CERN, Switzerland}\\
       \email{g.louppe@cern.ch}
\alignauthor
Hussein T. Al-Natsheh\\
       \affaddr{ISH-LYON (USR 3385), CNRS, France}\\
       \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
\alignauthor
Mateusz Susik\\
       \affaddr{University of Warsaw}\\
       \email{msusik@student.uw.edu.pl}
\alignauthor
\and
Eamonn Maguire\\
       \affaddr{CERN, Switzerland}\\
       \email{eamonn.james.maguire@cern.ch}
}

@@

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by the same person, accounting
for potential homonyms and/or synonyms.
Among solutions to this problem, digital libraries are increasingly offering tools
for authors to manually curate their publications and claim those that are theirs.
Indirectly, these tools allow for the inexpensive collection of large annotated training
data, which can be further leveraged to build a complementary automated
disambiguation system capable of inferring patterns for identifying
publications written by the same person.
Building on more than 1 million publicly released crowdsourced annotations,
we propose an automated author disambiguation solution exploiting this data (i) to learn
an accurate classifier for identifying coreferring authors and (ii) to guide the clustering
of scientific publications by distinct authors in a semi-supervised way.
To the best of our knowledge, our analysis is the first to be carried out on data of
this size and coverage.
With respect to the state of the art, we validate the general pipeline used in most existing
solutions, and improve by: (i) proposing phonetic-based blocking strategies, thereby
increasing recall; and (ii) adding strong ethnicity-sensitive features for learning a linkage
function, thereby tailoring disambiguation to non-Western author names whenever necessary. (iii) Showing the importance of balancing negative and positive examples when learning the linkage function.
In addition to releasing the software implementation of our improved pipeline, we also published the verified dataset to ease the comparison with other researchers who are interested in further contribution. 
\end{abstract}
